MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
Found FGA and FG% for each individual player

# Trying to reshape...

library(reshape)
game <- cast(data = df, GAME_ID1 ~ SHOT_RESULT)
View(game)

@@

Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
for(i in 21400001:21400908){
  j = i - 21400001 +1 # 
  game <- df[, df[, "GAME_ID1"] == i]
  home <- game[, game["LOCATION"] == "H"]
  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
  away <- game[, game["LOCATION"] == "A"]
  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
  FG_Percentage[j] <- home.p
  FG_Percentage[j + 1] = away.p
  Team[j] = "H"
  Team[j + 1] = "A"
}

>>>>

# Reshape the dataframe

game <- cast(data = df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + LOCATION + player_name + W ~ FGM)

# Field Goal Attempts

game[, "FGA"] <- NA
for(i in 1:nrow(game)){
  game[i, "FGA"] <- game[i, "1"] + game[i, "0"]
}

# find Feild Goal % of each indivudual player in that match

game[, "FG%"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG%"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}

@@

#Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
#FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
#for(i in 21400001:21400908){
#  j = i - 21400001 +1 # 
#  game <- df[, df[, "GAME_ID1"] == i]
#  home <- game[, game["LOCATION"] == "H"]
#  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
#  away <- game[, game["LOCATION"] == "A"]
#  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
#  FG_Percentage[j] <- home.p
#  FG_Percentage[j + 1] = away.p
#  Team[j] = "H"
#  Team[j + 1] = "A"
#}
